\cvsection{Education}

\cvevent{\href{https://mavaji.github.io/assets/docs/sharif-cl.pdf}{M.Sc.} in Computational Linguistics}{\href{http://www.sharif.edu}{Sharif University of Technology}}{Sep. 2010 -- Jul. 2012}{}

\divider

\cvevent{\href{https://mavaji.github.io/assets/docs/sharif-ce.pdf}{M.Sc.} in Computer Engineering}{\href{http://www.sharif.edu}{Sharif University of Technology}}{Sep. 2004 -- Sep. 2006}{}

\divider

\cvevent{\href{https://mavaji.github.io/assets/docs/iust-bs.pdf}{B.Sc.} in Computer Engineering}{\href{http://www.iust.ac.ir}{Iran University of Science and Technology}}{Sep. 2000 -- Sep. 2004}{}

\divider

\cvevent{Architecture}{\href{http://www.iust.ac.ir}{Iran University of Science and Technology}}{Sep. 1999 -- Jun. 2000}{}
%-----------------------------------------------------------------------------------------------------------------------
\cvsection{Technical Skills}
Scala, Java, Python, Haskell, Kotlin, C, JavaScript

\divider\smallskip

Apache Spark, Apache Kafka

\divider\smallskip

Apache Cassandra, MongoDB, Redis, Elasticsearch, MySQL, Oracle Database

\divider\smallskip

GNU/Linux, Docker, Kubernetes, Jenkins, Git, Kibana, Grafana

\divider\smallskip

Spring Framework, Spring Boot, Spring Cloud, Spring Data, Spring Web Services, Spring Security, Spring Web Flow

\divider\smallskip

Object-Oriented, Functional, Reactive, Concurrent and Parallel Programming, Test-Driven Development, Design Patterns, Software Architecture
%-----------------------------------------------------------------------------------------------------------------------


