%-----------------------------------------------------------------------------------------------------------------------
\cvsection{Test Scores}

\cvevent{English}{\href{https://mavaji.github.io/assets/docs/TOEFL.pdf}{TOEFL iBT, 103/120}}{Dec. 10, 2011}{}
\begin{itemize}
    \item {Reading: 28/30}
    \item {Listening: 28/30}
    \item {Speaking: 20/30}
    \item {Writing: 27/30}
\end{itemize}

\divider

\cvevent{French}{\href{https://mavaji.github.io/assets/docs/DELF-B1.pdf}{DELF B1, 79.5/100}}{Aug. 24, 2010}{}
\begin{itemize}
    \item {Production Écrite: 19/25}
    \item {Compréhension Écrite: 21/25}
    \item {Production Orale: 18.5/25}
    \item {Compréhension Orale: 21/25}
\end{itemize}

\divider

\cvevent{GRE}{\href{https://mavaji.github.io/assets/docs/GRE.pdf}{GRE General Test}}{Nov. 19, 2011}{}
\begin{itemize}
    \item {Verbal Reasoning: 147/170}
    \item {Quantitative Reasoning: 158/170}
    \item {Analytical Writing: 4/6}
\end{itemize}

%% Yeah I didn't spend too much time making all the
%% spacing consistent... sorry. Use \smallskip, \medskip,
%% \bigskip, \vpsace etc to make ajustments.
\medskip
%-----------------------------------------------------------------------------------------------------------------------
\cvsection{Teaching}
\cvevent{Laboratory Instructor}{\href{http://ce.sharif.edu/}{Sharif University of Technology}}{Feb. 2006 -- Jun. 2006}{}
\begin{itemize}
    \item
    {Network and Data Communication Laboratory}
    \item
    {Logic Circuit Design Laboratory}
\end{itemize}

\divider

\cvevent{Teaching Assistant}{\href{http://ce.sharif.edu/}{Sharif University of Technology}}{Feb. 2005 -- Jun. 2005}{}
\begin{itemize}
    \item
    {Logic Circuit Design}
\end{itemize}

\divider

\cvevent{Teaching Assistant}{\href{http://ce.iust.ac.ir/}{Iran University of Science and Technology}}{Feb. 2003 -- Jun. 2003}{}
\begin{itemize}
    \item
    {Artificial Intelligence}
\end{itemize}

\divider

\cvevent{Teaching Assistant}{\href{http://ce.iust.ac.ir/}{Iran University of Science and Technology}}{Sep. 2002 -- Jun. 2003}{}
\begin{itemize}
    \item
    {Electrical Circuits II}
\end{itemize}
%-----------------------------------------------------------------------------------------------------------------------
